PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$

### 2014-09-11 qfenv_paper/qf_environment.tex
more edits to the comparison to lit

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% COMPARISON TO LITERATURE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison to Literature}
Although a direct comparison with other results is impossible due to our sample specific methodology, a number of results from literature have investigated the quiescent fraction. In this section we compare our $f_{\rm{Q}}$ results from above to a number of these results, specifically from SDSS and zCOSMOS, with comparably defined samples and analogous environment classifications.

@@

Furthermore, in Section \ref{sec:qffit}, by comparing the $f_{\rm{Q}}$ evolution between the lowest density environment and the highest density environment, we found moderate evidence for the existence of environment dependent quenching mechanisms.

@@

In addition to the overall range of the $f_{\rm{Q}}$, in Section \ref{sec:qfevol} we addressed that for both low and high density environments, $f_{\rm{Q}}$ increases as redshift decreases. This general trend is in good agreement with \cite{Iovino:2010aa}, which finds a similar increase in $1-f_{\rm{blue}}$ over cosmic time for $\mathcal{M} < 10^{10.9} \mathcal{M}_{\odot}$. However, in contrast to our $f_{\rm{Q}}$ redshift evolution, \cite{Kovac:2014aa} presents a notable decrease in $f_{\rm{red}}$ over cosmic time for low environment. Even for their galaxies in high density environments, \cite{Kovac:2014aa} finds no significant increase in $f_{\rm{red}}$ with cosmic time.

An environment dependence of the $f_{\rm{Q}}$ evolution is also observed in \cite{Iovino:2010aa} - also plotted in Figure \ref{fig:qffit_comp}. However, in addition to a much more pronounced distinction between the group and isolated $f_{\rm{Q}}$ evolution, they find the opposite environment dependence. Unlike our results, which find a greater $f_{\rm{Q}}$ evolution at higher density environments, \cite{Iovino:2010aa} finds a much greater evolution for isolated galaxies.

\cite{Kovac:2014aa} finds a similar environment dependence on the total $f_{\rm{Q}}$ evolution as our results, with a greater $f_{\rm{Q}}$ evolution for high density environments. Unfortunately, contrary to our results, \cite{Kovac:2014aa} finds that $f_{\rm{Q}}$ decreases for both environments over cosmic time. The negative slope of the $f_{\rm{Q}}$ evolution is enhanced in Figure \ref{fig:qffit_comp} due to the galaxy classification correction we impose, but even without the correction (not shown), in their best-fit values, \cite{Kovac:2014aa} finds a decreasing $f_{\rm{Q}}$ evolution.

While the zCOSMOS survey provides more precise spectroscopic redshift than our sample derived from PRIMUS, our sample provides significantly larger statistics. As listed in Table \ref{tab:subsample}, our sample consists of $64,026$ galaxies from SDSS and $12,861$ galaxies from PRIMUS totaling $76887$ galaxies. Meanwhile \cite{Iovino:2010aa} has $914$ galaxies with $\mathcal{M} > 10^{10.3} \mathcal{M}_{\odot}$ and $0.1 < z < 0.6$ and $1033$ galaxies with $\mathcal{M} > 10^{10.6} \mathcal{M}_{\odot}$ and $0.1 < z < 0.8$. But for the actual sample used to obtain the best-fit $f_{\rm{Q}}$ values in Figure \ref{fig:qffit_comp} \cite{Iovino:2010aa} has $617$ galaxies. The more recent \cite{Kovac:2014aa} provides larger statistics with $2340$ galaxies with $0.1 < z < 0.4$ and $2448$ galaxies with $0.4 < z < 0.7$; however falls short of our SDSS-{\em GALEX} and PRIMUS sample. Furthermore, our sample derived from SDSS-{\em GALEX} and PRIMUS cover $2505 \rm{deg}^2$ and $5.5 \rm{deg}^2$ respectively. Compared to zCOSMOS, which covers $1.7 \rm{deg}^2$ of the sky, our sample provides significantly greater sky coverage and thus less affected by cosmic variance. 
% zCOSMOS has more precise redshift but PRIMUS has it beat in terms of sample size and coverage of the sky 5.5 deg^2 vs 1.7 deg^2
% Kovac: 1.7 deg^2, 0.1 < z < 0.4 2340 and 0.4 < z < 0.7 2448. Most of the data points have errors of +/- 0.1, at least +/-0.05
% Iovino: 1.7 deg^2  617 galaxies in 10.3 < M < 10.8 and 0.1 < z < 0.6. Errors are +/1 0.1

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% COMPARISON TO LITERATURE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison to Literature}
Although a direct comparison with other results is difficult due to our sample specific methodology, a number of results from literature have investigated the quiescent fraction in comparable fashions. In this section we compare our $f_{\rm{Q}}$ results from above to a number of these results, specifically from SDSS and zCOSMOS, with similarly defined samples and analogous environment classifications.

@@

Furthermore, in Section \ref{sec:qffit}, our comparison of the $f_{\rm{Q}}$ evolution between the lowest density environment and the highest density environment revealed a modicum of evidence for the existence of environment dependent quenching mechanisms. The same comparison on zCOSMOS results (\citealt{Iovino:2010aa, Kovac:2014aa}) present trends inconsistent with our findings. First, comparing the high (red) and low (blue) density environments for \cite{Iovino:2010aa} in Figure \ref{fig:qffit_comp} shows that there is indeed pronounced discrepancies between the $f_{\rm{Q}}$ evolution in different environments. Group galaxies in \cite{Iovino:2010aa} have higher overall $f_{\rm{Q}}$ than isolated galaxies. However, unlike our results, which find a greater $f_{\rm{Q}}$ evolution at higher density environments, \cite{Iovino:2010aa} finds the opposite environment dependence that there is a significantly greater $f_{\rm{Q}}$ evolution for isolated galaxies.

Next, \cite{Kovac:2014aa} also find that overall $f_{\rm{Q}}$ in high density is greater than low density environments. Like their low density environment $f_{\rm{Q}}$ evolution, $f_{\rm{Q}}$ in high density environment decreases over cosmic time between their two redshift bins. Although the decrease in $f_{\rm{Q}}$ over cosmic time conflicts with our results, \cite{Kovac:2014aa} finds a greater (less negative) $f_{\rm{Q}}$ evolution in high density environment over low density environment, suggesting an environment dependence that is in the same direction as our results. We note that the negative slopes of the $f_{\rm{Q}}$ evolution in both environments are enhanced in Figure \ref{fig:qffit_comp} due to the galaxy classification correction we impose to the \cite{Kovac:2014aa} results. However, even without the correction (not shown), in their best-fit $f_{\rm{Q}}$ results, the same evolutionary trends mentioned above are observed.

While the zCOSMOS survey provides more precise spectroscopic redshift than PRIMUS, our sample provides a significantly larger statistics. As listed in Table \ref{tab:subsample}, even after our edge effect cuts and stellar mass completeness limits, our sample consists of $12,861$ galaxies from PRIMUS over $0.2< z< 0.8$ and $64,026$ galaxies from SDSS over $0.05 < z < 0.12$. Meanwhile, \cite{Iovino:2010aa} has $914$ galaxies with $\mathcal{M} > 10^{10.3} \mathcal{M}_{\odot}$ over $0.1 < z < 0.6$ and $1033$ galaxies with $\mathcal{M} > 10^{10.6} \mathcal{M}_{\odot}$ over $0.1 < z < 0.8$. But for the actual sample used to obtain the best-fit $f_{\rm{Q}}$ values in Figure \ref{fig:qffit_comp} \cite{Iovino:2010aa} has $617$ galaxies. In comparison, our PRIMUS sample alone contains $> 20$ times the number of galaxies. Given the difference in sample size, much of the evolutionary trend discrepancy between the \cite{Iovino:2010aa} results and our results could be attributed to the limited statics in \cite{Iovino:2010aa}.

The more recent \cite{Kovac:2014aa} provides larger statistics with $2,340$ galaxies in their lower redshift bin ($0.1 < z < 0.4$) and $2,448$ galaxies in their higher redshift bin ($0.4 < z < 0.7$). Although the sample falls short of our PRIMUS sample, which contains over two times the number of galaxies, it contains sufficient statistics for a more s

In addition to the number of galaxies, our sample covers a larger portion of the sky. Our SDSS-{\em GALEX} sample covers $2,505 \rm{deg}^2$. More comparably, our PRIMUS sample covers $5.5 \rm{deg}^2$, which is over 3 times the sky coverage of zCOSMOS, $1.7 \rm{deg}^2$.

@@

While the zCOSMOS survey provides more precise spectroscopic redshift than our sample derived from PRIMUS, our sample provides significantly larger statistics. As listed in Table \ref{tab:subsample}, our sample consists of $64,026$ galaxies from SDSS and $12,861$ galaxies from PRIMUS totaling $76887$ galaxies. Meanwhile \cite{Iovino:2010aa} has $914$ galaxies with $\mathcal{M} > 10^{10.3} \mathcal{M}_{\odot}$ and $0.1 < z < 0.6$ and $1033$ galaxies with $\mathcal{M} > 10^{10.6} \mathcal{M}_{\odot}$ and $0.1 < z < 0.8$. But for the actual sample used to obtain the best-fit $f_{\rm{Q}}$ values in Figure \ref{fig:qffit_comp} \cite{Iovino:2010aa} has $617$ galaxies. The more recent \cite{Kovac:2014aa} provides larger statistics with $2340$ galaxies with $0.1 < z < 0.4$ and $2448$ galaxies with $0.4 < z < 0.7$; however falls short of our PRIMUS sample. Furthermore, our sample derived from SDSS-{\em GALEX} and PRIMUS cover $2505 \rm{deg}^2$ and $5.5 \rm{deg}^2$ respectively. Compared to zCOSMOS, which covers $1.7 \rm{deg}^2$ of the sky, our sample provides significantly greater sky coverage and thus less affected by cosmic variance. 
% zCOSMOS has more precise redshift but PRIMUS has it beat in terms of sample size and coverage of the sky 5.5 deg^2 vs 1.7 deg^2
% Kovac: 1.7 deg^2, 0.1 < z < 0.4 2340 and 0.4 < z < 0.7 2448. Most of the data points have errors of +/- 0.1, at least +/-0.05
% Iovino: 1.7 deg^2  617 galaxies in 10.3 < M < 10.8 and 0.1 < z < 0.6. Errors are +/1 0.1
